Figures and tables for paper

### 2021-12-09 analysis/04_figs-tables.Rmd
Completing contrasts

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(magrittr)
library(tidybayes)
library(broom)
# library(ggridges)
library(ggraph)
library(ggdag)
library(pander)
library(patchwork)
library(scales)
library(here)

@@

# Load draws
intercept <- 1                            # Intercept-only
interactions <- 1                         # Include interactions with the intercept-only model?
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

Another approach to address the hypotheses is to plot contrasts.

```{r}
#storing intercept draws for easier reference
draws_intercepts <- draws
```

@@

```{r branding-contrasts}
# Pull the posterior draws for the organizations and compute contrasts
draws_intercepts <- draws

contrasts <- tibble(
  amnesty = draws %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty = oxfam - amnesty,
    oxfam_greenpeace = oxfam - greenpeace,
    red_cross_amnesty = red_cross - amnesty,
    red_cross_greenpeace = red_cross - greenpeace,
  )

# Plot the contrasts
contrasts %>%
  pivot_longer(oxfam_amnesty:red_cross_greenpeace, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace. However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam. In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International.

@@

```{r crackdown-contrasts-a}
# Pull the posterior draws for government crackdown
# Reference Level = Friendly relationship with government
draws_intercepts <- draws

contrasts <- tibble(
  under_crackdown = draws %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
  )

# Plot the contrasts
contrasts %>%
  pivot_longer(under_crackdown:criticized, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism. This decreased likelihood to donate is also greater for NGOs under crackdown compared to those under criticism.

@@

```{r crackdown-contrasts-b}
# Overwrite draws with the appropriate interaction data

draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_2b.rds"))

# Pull the posterior draws for organization*government crackdown interaction
# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  fin_transparency = draws %>% filter(i == 8)%>% select(Gamma) %>% pull(),
  accountability = draws %>% filter(i == 9) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    oxfam_amnesty_criticized = (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),

    oxfam_greenpeace_criticized = (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),

    red_cross_amnesty_criticized = (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),

    red_cross_greenpeace_criticized = (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),

    oxfam_amnesty_crackdown = (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),

    oxfam_greenpeace_crackdown = (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),

    red_cross_amnesty_crackdown = (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),

    red_cross_greenpeace_crackdown = (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(oxfam_amnesty_criticized:red_cross_greenpeace_crackdown, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions. The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown. All other contrasts do not contain 0 within their credibility interval.

@@

```{r issue-contrasts-a}
# Pull the posterior draws for issue area
# Reference Level = Emergency Response
draws <- draws_intercepts

contrasts <- tibble(
  environment = draws %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
  )

# Plot the contrasts
contrasts %>%
  pivot_longer(environment:refugee_relief, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

Donors appear to be sensitive to NGO issue area when they are considering to donate. Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations. While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, which was contrary to our expectations. It is worth noting that there is some overlap between the intervals of the issue areas, which would suggest that their effect isn't as significant as other factors.

@@

```{r issue-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

# Pull the posterior draws for government crackdown*issue area interaction
# Reference Level = Friendly relationship with government
# Reference Level = Emergency Response

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_humanrights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
    criticized_emergency_environment = (criticized) - (criticized + environment + criticized_environment),

  criticized_emergency_humanrights = (criticized) - (criticized + human_rights + criticized_humanrights),

  crackdown_emergency_environment = (crackdown) - (crackdown + environment + crackdown_environment),

  crackdown_emergency_humanrights = (crackdown) - (crackdown + human_rights + crackdown_humanrights),

  criticized_refugee_environment = (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),

  criticized_refugee_humanrights = (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_humanrights),

  crackdown_refugee_environment = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),

  crackdown_refugee_humanrights = (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_humanrights)
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_emergency_environment:crackdown_refugee_humanrights, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

@@

Per our hypothesis, we expected to see the contrasts of the posterior distributions to be positive. However, only the contrasts between emergency response and the more contentious issue areas (environment and human rights) were positive, while contrasts between refugee relief and the more contentious issue areas were negative. Looking at all the contrasts, crackdown_refugee_environment, criticized_refugee_environment, and crackdown_emergency_humanrights contained 0 within their credibility interval.

@@

```{r funding-contrasts-a}
# Pull the posterior draws for funding sources
# Reference Level = Funded primarily by many small private donations
draws <- draws_intercepts
contrasts <- tibble(
  few_wealthy_private_donors = draws %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
  )

# Plot the contrasts
contrasts %>%
  pivot_longer(few_wealthy_private_donors:government_grants, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis04a.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

As stated in the hypothesis, donors show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.

@@

```{r funding-contrasts-b}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))

# Pull the posterior draws for government crackdown*funding sources interaction
# Reference Level = Friendly relationship with government
# Reference Level = Funded primarily by many small private donations

contrasts_int <- tibble(
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
) %>% mutate(
  criticized_wealthydonors = (criticized) - (criticized + few_wealthy_private_donors + criticized_wealthydonors),

  criticized_grants = (criticized) - (criticized + government_grants + criticized_grants),

  crackdown_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + crackdown_wealthydonors),

  crackdown_grants = crackdown - (crackdown + government_grants + crackdown_grants)
)

# Plot the contrasts
contrasts_int %>%
  pivot_longer(criticized_wealthydonors:crackdown_grants, names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Difference in Attribute Levels", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis04b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)

All of the contrasts are positive and none of them contain 0 within their credibility interval, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.

@@

```{r funding-contrasts-c}
# Overwrite draws with the appropriate interaction data
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
# Draws for lower order interactions
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

# Pull the posterior draws for issue area*government crackdown*funding sources interaction
# Reference Level = Funded primarily by many small private donations
# Reference Level = Friendly relationship with government

contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws_3b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_humanrights = draws_3b %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws_3b %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws_4b %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws_4b %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  emergency_crackdown_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  emergency_crackdown_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  environment_crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  environment_crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_wealthydonors = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  humanrights_crackdown_grants = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  refugee_crackdown_wealthydonors = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  refugee_crackdown_grants = draws %>% filter(i == 21) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
  emergency_humanrights_wealthydonors = (crackdown) - (crackdown + few_wealthy_private_donors + human_rights + crackdown_humanrights + crackdown_wealthydonors + humanrights_crackdown_wealthydonors),

>>>>

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(magrittr)
library(tidybayes)
library(broom)
library(ggridges)
library(ggraph)
library(ggdag)
library(pander)
library(patchwork)
library(scales)
library(here)

@@

# Load draws
intercept <- 1                            # Intercept-only
interactions <- 0                         # Include interactions with the intercept-only model
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

To formally answer the hypotheses, we compute contrasts of the marginal posteriors. First, we need the intercept-only draws and associated levels.

```{r intercept-draws}
# Import draws
draws_intercept <- read_rds(here::here("data", "raw_data", "posterior_draws", "intercept.rds")) %>% 
  mutate(model = "Intercept only")

# Join level and covariate labels to draws
draws_intercept <- draws_intercept %>% 
  left_join(level_lookup, by = "i")
```

@@

```{r contrasts-hypothesis01}
# Compute the contrasts
contrasts <- tibble(
  amnesty = draws_intercept %>% filter(level == "Amnesty International") %>% select(Gamma) %>% pull(),
  greenpeace = draws_intercept %>% filter(level == "Greenpeace") %>% select(Gamma) %>% pull(),
  oxfam = draws_intercept %>% filter(level == "Oxfam") %>% select(Gamma) %>% pull(),
  red_cross = draws_intercept %>% filter(level == "Red Cross") %>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "oxfam - amnesty" = oxfam - amnesty,
    "oxfam - greenpeace" = oxfam - greenpeace,
    "red cross - amnesty" = red_cross - amnesty,
    "red cross - greenpeace" = red_cross - greenpeace,
  )

# Plot the contrasts
contrasts %>%
  pivot_longer("oxfam - amnesty":"red cross - greenpeace", names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors are indeed more likely to donate to Red Cross compared to Amnesty International and Greenpeace. However, compared to Amnesty International and Greenpeace, donors are less likely to donate to Oxfam. In fact, there is a negligible difference between donors likelihood to donate to Oxfam and Amnesty International. This might be because the population we sampled from was specifically in the United States, where Oxfam and Amnesty may be less well known.

@@

```{r contrasts-hypothesis02a}
# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts <- tibble(
  "crackdown - friendly" = draws_intercept %>% filter(level == "Under crackdown") %>% select(Gamma) %>% pull(),
  "criticized - friendly" = draws_intercept %>% filter(level == "Criticized") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer("crackdown - friendly":"criticized - friendly", names_to = "level", values_to = "Gamma") %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Contrary to our hypothesis, donors showed decreased willingness to donate to NGOs that are facing government crackdown or criticism relative to NGOs that have a friendly relationship with the government, with this decreased likelihood to donate greater for NGOs under crackdown compared to those being criticized.

@@

```{r contrasts-hypothesis02b}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_2b.rds"))

# Reference Level = Friendly relationship with government
# Compute the contrasts
contrasts_int <- tibble(
  amnesty = draws %>% filter(i == 1) %>% select(Gamma) %>% pull(),
  greenpeace = draws %>% filter(i == 2) %>% select(Gamma) %>% pull(),
  oxfam = draws %>% filter(i == 3) %>% select(Gamma) %>% pull(),
  red_cross = draws %>% filter(i == 4)%>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  amnesty_criticized = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  greenpeace_criticized = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  oxfam_criticized = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  red_cross_criticized = draws %>% filter(i == 17)%>% select(Gamma) %>% pull(),
  amnesty_crackdown = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  greenpeace_crackdown = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
  oxfam_crackdown = draws %>% filter(i == 20) %>% select(Gamma) %>% pull(),
  red_cross_crackdown = draws %>% filter(i == 21)%>% select(Gamma) %>% pull()
) %>% 
  mutate(
    "criticized oxfam - criticized amnesty" = 
      (oxfam + criticized + oxfam_criticized) - (amnesty + criticized + amnesty_criticized),
    "criticized oxfam - criticized greenpeace" = 
      (oxfam + criticized + oxfam_criticized) - (greenpeace + criticized + greenpeace_criticized),
    "criticized red cross - criticized amnesty" = 
      (red_cross + criticized + red_cross_criticized) - (amnesty + criticized + amnesty_criticized),
    "criticized red cross - criticized green peace" = 
      (red_cross + criticized + red_cross_criticized) - (greenpeace + criticized + greenpeace_criticized),
    "crackdown oxfam - crackdown amnesty" = 
      (oxfam + crackdown + oxfam_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    "crackdown oxfam - crackdown greenpeace" = 
      (oxfam + crackdown + oxfam_crackdown) - (greenpeace + crackdown +  greenpeace_crackdown),
    "crackdown red cross - crackdown amnesty" = 
      (red_cross + crackdown + red_cross_crackdown) - (amnesty + crackdown +  amnesty_crackdown),
    "crackdown red cross - crackdown greenpeace" = 
      (red_cross + crackdown + red_cross_crackdown) - (greenpeace + crackdown + greenpeace_crackdown)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "criticized oxfam - criticized amnesty":"crackdown red cross - crackdown greenpeace", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Although donors show significantly more willingness to donate to Red Cross when they are criticized or under crackdown from the host government, donors are less likely to donate to Oxfam under the same conditions. The only contrast which isn't statistically significant is the difference between Oxfam and Amnesty when both are under crackdown.

@@

```{r contrasts-hypothesis03a}
# Reference Level = Emergency Response
# Compute the contrasts
contrasts <- tibble(
  "environment - emergency" = draws_intercept %>% filter(level == "Environment") %>% select(Gamma) %>% pull(),
  "human rights - emergency" = draws_intercept %>% filter(level == "Human rights") %>% select(Gamma) %>% pull(),
  "refugee relief - emergency" = draws_intercept %>% filter(level == "Refugee relief") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer(
    "environment - emergency":"refugee relief - emergency", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Donors appear to be sensitive to NGO issue area when they are considering to donate. Emergency response was the most favored issue area by donors, and experienced the highest likelihood of receiving donations. While this partially matches the claim of the hypothesis, donors showed the least likelihood to donate to refugee relief NGOs, although this is not significantly different from their likelihood of donating for environmental causes. In other words, refugee relief appears to be as contentious as environment.

@@

```{r contrasts-hypothesis03b}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))

# Reference Level = Emergency Response
# Compute the contrasts
contrasts_int <- tibble(
  environment = draws %>% filter(i == 5) %>% select(Gamma) %>% pull(),
  human_rights = draws %>% filter(i == 6) %>% select(Gamma) %>% pull(),
  refugee_relief = draws %>% filter(i == 7) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_environment = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_human_rights = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  criticized_refugee = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_environment = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
  crackdown_human_rights = draws %>% filter(i == 18) %>% select(Gamma) %>% pull(),
  crackdown_refugee = draws %>% filter(i == 19) %>% select(Gamma) %>% pull(),
) %>% 
  mutate(
    "criticized emergency - criticized environment" = 
      (criticized) - (criticized + environment + criticized_environment),
    "criticized emergency - criticized human rights" = 
      (criticized) - (criticized + human_rights + criticized_human_rights),
    "crackdown emergency - crackdown environment" = 
      (crackdown) - (crackdown + environment + crackdown_environment),
    "crackdown emergency - crackdown human rights" = 
      (crackdown) - (crackdown + human_rights + crackdown_human_rights),
    "criticized refugee relief - criticized environment" = 
      (criticized + refugee_relief + criticized_refugee) - (criticized + environment + criticized_environment),
    "criticized refugee relief - criticized human rights" = 
      (criticized + refugee_relief + criticized_refugee) - (criticized + human_rights + criticized_human_rights),
    "crackdown refugee relief - crackdown environment" = 
      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + environment + crackdown_environment),
    "crackdown refugee relief - crackdown human rights" = 
      (crackdown + refugee_relief + crackdown_refugee) - (crackdown + human_rights + crackdown_human_rights)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "criticized emergency - criticized environment":"crackdown refugee relief - crackdown human rights", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

@@

Per our hypothesis, we expected to see the contrasts of the posterior distributions to be positive. However, only the contrasts between emergency response and the more contentious issue areas (environment and human rights) were positive, while contrasts between refugee relief and the more contentious issue areas were negative. Here the issue area itself matters far more than the relationship with the host government.

@@

```{r contrasts-hypothesis04a}
# Reference Level = Funded primarily by many small private donations
# Compute the contrasts
contrasts <- tibble(
  "wealthy donors - small donors" = draws_intercept %>% filter(level == "Handful of wealthy private donors") %>% select(Gamma) %>% pull(),
  "government grants - small donors" = draws_intercept %>% filter(level == "Government grants") %>% select(Gamma) %>% pull()
)

# Plot the contrasts
contrasts %>%
  pivot_longer(
    "wealthy donors - small donors":"government grants - small donors", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis04a.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

Donors indeed show increased willingness to donate to NGOs funded by numerous small private donors, as opposed to those funded by a handful of wealthy private donors or government grants.

@@

```{r contrasts-hypothesis04b}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))

# Reference Level = Funded primarily by many small private donations
# Compute the contrasts
contrasts_int <- tibble(
  few_wealthy_private_donors = draws %>% filter(i == 10) %>% select(Gamma) %>% pull(),
  government_grants = draws %>% filter(i == 11) %>% select(Gamma) %>% pull(),
  criticized = draws %>% filter(i == 12)%>% select(Gamma) %>% pull(),
  crackdown = draws %>% filter(i == 13) %>% select(Gamma) %>% pull(),
  criticized_wealthydonors = draws %>% filter(i == 14) %>% select(Gamma) %>% pull(),
  criticized_grants = draws %>% filter(i == 15) %>% select(Gamma) %>% pull(),
  crackdown_wealthydonors = draws %>% filter(i == 16) %>% select(Gamma) %>% pull(),
  crackdown_grants = draws %>% filter(i == 17) %>% select(Gamma) %>% pull(),
) %>% mutate(
  "criticized small donors - criticized wealthy donors" = 
    (criticized) - (few_wealthy_private_donors + criticized + criticized_wealthydonors),
  "criticized small donors - criticized government grants" = 
    (criticized) - (government_grants + criticized + criticized_grants),
  "crackdown small donors - crackdown wealthy donors" = 
    (crackdown) - (few_wealthy_private_donors + crackdown + crackdown_wealthydonors),
  "crackdown small donors - crackdown government grants" = 
    (crackdown) - (government_grants + crackdown + crackdown_grants)
  )

# Plot the contrasts
contrasts_int %>%
  pivot_longer(
    "criticized small donors - criticized wealthy donors":"crackdown small donors - crackdown government grants", 
    names_to = "level", values_to = "Gamma"
  ) %>% 
  ggplot(aes(x = Gamma, y = level)) +
  stat_halfeye(.width = .95) +
  geom_vline(xintercept = 0, color = "grey") +
  labs(y = "Contrasts", x = "Difference in Gammas")

# Save plot
ggsave(
  "contrasts_hypothesis04b.png",
  path = here::here("analysis", "output", "figures"),
  width = 12,
  height = 6,
  units = "in"
)
```

All of the contrasts are positive and significant, which supports our hypothesis that donors are more willing to donate to organizations supported by many small private donors and are under criticism or crackdown.

@@

```{r contrasts-hypothesis04c}
# Import the appropriate interaction draws
draws <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4c.rds"))
draws_4b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_4b.rds"))
draws_3b <- read_rds(here::here("data", "raw_data", "posterior_draws", "interactions_3b.rds"))
